Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-09-27 LaTeX_paper/paper.tex
fix paper error

% to include svg images
\usepackage{svg}

% settings for how to indend the page when neaded
\newenvironment{indented_section}
  {\adjustwidth{3em}{0pt}}
  {\endadjustwidth}

@@

\section{Abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for "digital" jigsaw puzzles. However, the counterpart:
the "real world" jigsaw puzzle, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

The puzzle problem can be divided into two separate components: the "Comparator"
whose objective is to determine whether two sides of two pieces fit together,
and the "Solver" whose objective is to use the information provided
by the comparator to find the best way to fit some pieces together.

@@

There is  another important distinction between different types of puzzles.
They can be divided into “digital” and “real world” jigsaw puzzles.
\label{document:DigitalVSReal}

@@

    \subsubsection{The Splitter:} This component takes as input one or more images
    containing all the pieces. It then split all the pieces from each other,
    9and split each piece into his four sides.\label{document:splitter}

@@

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls in the “binary comparison” category~\ref{document:comparator}.
And can be used to understand the strength and weaknesses
of this approach.\newline
The main benefit of this approach is speed,  having a binary comparison allows
some specific optimization, in particular the use of some graph theory techniques.\newline
The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
minimum for jigsaw puzzle solving, according to the study:
“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”.\newline
The negative aspect might be the accuracy, since by using only two states
(match or not match) some informations are lost, compared to a non binary comparison.
To quantify accuracy the paper used the “neighbors comparison” metric,
which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
\label{document:GCL}

@@

\begin{center}
  \includesvg[height=3.75in]{pictures/match_metrics_vs_threshold_used.svg}
\end{center}

>>>>

% to include svg images
%\usepackage{svg}

% settings for how to indent the page when needed
\newenvironment{indented_section}
  {\adjustwidth{3em}{0pt}}
  {\endadjustwidth}

@@

\section{Abstract}
This paper examines the Jigsaw puzzle problem,
which has already been extensively studied in the literature.
Several algorithms with efficient time complexity have been developed
specifically for 'digital' jigsaw puzzles. However, the counterpart:
the 'real world' jigsaw puzzle, has received relatively little attention
in the literature. While some small-scale projects have addressed this issue,
we were unable to find any papers discussing it.

The puzzle problem can be divided into two separate components: the 'Comparator'
whose objective is to determine whether two sides of two pieces fit together,
and the 'Solver' whose objective is to use the information provided
by the comparator to find the best way to fit some pieces together.

@@

There is  another important distinction between different types of puzzles.
They can be divided into “digital” and “real world” jigsaw puzzles.\label{document:DigitalVSReal}

@@

    \subsubsection{The Splitter:} This component takes as input one or more images
    containing all the pieces. It then split all the pieces from each other,
    and split each piece into his four sides.\label{document:splitter}

@@

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls in the “binary comparison” category~\cref{document:comparator}.
And can be used to understand the strength and weaknesses
of this approach.\newline
The main benefit of this approach is speed,  having a binary comparison allows
some specific optimization, in particular the use of some graph theory techniques.\newline
The  algorithm has a time complexity of ruffly \(O(N^2)\). Which is in line with the theoretical
minimum for jigsaw puzzle solving, according to the study:
“No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}”.\newline
The negative aspect might be the accuracy, since by using only two states
(match or not match) some informations are lost, compared to a non binary comparison.
To quantify accuracy the paper used the “neighbors comparison” metric,
which “calculates the percentage of pairs of image patches that are matched correctly”.\newline
\label{document:GCL}

@@

\begin{figure}[h]
    \caption{match metrics vs threshold used}\label{fig:match_metrics_vs_threshold_used}
    \centering
    \includegraphics[height=0.5\textwidth]{pictures/match_metrics_vs_threshold_used.png}
\end{figure}
